Models

### 2022-04-27 analysis/05_model_metrics.Rmd
Make sure variable names propogate through

# metric_model_table <- bind_rows(mod_results %>% filter(is.na(warning)), 
#           bad_mod_results %>% filter(is.na(warning))) %>%
#   mutate(significant = case_when(
#     p.value > 0.05 | lower.CL < 0 & upper.CL > 0 ~ FALSE,
#     !is.na(p.value) | !is.na(lower.CL) ~ TRUE,
#     TRUE ~ NA
#   ))

@@

metric_model_table <- bind_rows(mod_results %>% filter(is.na(warning)), 
          bad_mod_results %>% filter(is.na(warning)),
          bad_mod_results2 %>% filter(is.na(warning))) %>%
  mutate(significant = case_when(
    p.value > 0.05 | lower.CL < 0 & upper.CL > 0 ~ FALSE,
    !is.na(p.value) | !is.na(lower.CL) ~ TRUE,
    TRUE ~ NA
  )) %>%
  select(-model)

@@

model_df <- metric_model_table %>%
  filter(model_id == "base") %>%
  select(metric, model, model_id) %>%
  group_by(metric, model_id) %>% 
  slice_head()

@@

#### Analizing slopes
Is slope a function of timeseries characteristics?
```{r}
library(multcomp)

@@

#All model estimates in one dataframe
slope_models <- bind_rows(duration_slope, startyear_slope)
pins::pin(slope_models, board = "github")

>>>>

@@

model_table <- bind_rows(mod_results %>% filter(is.na(warning)), 
          bad_mod_results %>% filter(is.na(warning)),
          bad_mod_results2 %>% filter(is.na(warning))) %>%
  mutate(significant = case_when(
    p.value > 0.05 | lower.CL < 0 & upper.CL > 0 ~ FALSE,
    !is.na(p.value) | !is.na(lower.CL) ~ TRUE,
    TRUE ~ NA
  )) #%>%
  #select(-model)

metric_model_table <- model_table %>% select(-model)

@@

model_df <- model_table %>%
  filter(model_id == "base") %>%
  select(metric, model, model_id) %>%
  group_by(metric, model_id) %>% 
  slice_head()

@@

#### Analizing slopes
Is slope a function of time series characteristics?
```{r}
library(multcomp)

@@

#All model estimates in one dataframe
# slope_models <- bind_rows(duration_slope, startyear_slope)
# pins::pin(slope_models, board = "github")
